---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# raadvrt

<!-- badges: start -->
<!-- badges: end -->

VERY MUCH WIP

Don't use the example code here it's very likely to crash your session. 

The goal of raadvrt is to collect VRT versions of raadtools data sources. 

WHY

- can GDALwarp a VRT (so we can get any layer we want in any projection/grid on-demand)
- VRT can be used by other systems (QGIS, Manifold, raster, terra, stars)

In theory we could parameterize the VRT creation, but that's lofty and this gets us heaps of leverage over raadtools itself

## GDALwarp

I mean with the GDAL API, via the [vapour](https://CRAN.r-project.org/package=vapour) package, not bound by any other GDAL wrapper or in-memory format. But, these will work through other GDAL wrappers as well. 



## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("AustralianAntarcticDivision/raadvrt")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(raadvrt)
## basic example code
```



## Code of Conduct
  
Please note that the raadvrt project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html). By contributing to this project, you agree to abide by its terms.
